### 2024-04-18 paper/paper.qmd
update paper

---
title: "Exploring Democratic Perceptions in South Korea"
subtitle: "An Analysis of Survey Data in 2016"
author: 
  - Hailey Jang 
thanks: "Code and data are available at: https://github.com/Hailey-Jang/How_South_Koreans_View_Democracy.git."
date: today
date-format: long
abstract: "This study explores the impact of globalization on democratic values and participation in South Korea by employing a linear regression model to analyze responses from a nationwide questionnaire on citizens' perceptions and engagement. It found that economic disparities and transformative political changes significantly influence citizens’ views on democracy and their participation levels. Through this quantitative analysis, the research uncovers a complex relationship between socio-economic factors and democratic perception, demonstrating how economic inequalities can diminish feelings of representation and reduce democratic participation. These findings underscore the importance of addressing economic and social inequalities to foster a more inclusive and participative democratic environment in South Korea, contributing to our broader understanding of how globalization shapes political systems worldwide."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
library(knitr)
library(kableExtra)
```

# Introduction

In South Korea, a nation where I was born and raised, the rapid and profound impacts of globalization have redefined the socio-economic and political landscape. As democracy inherently upholds the principle of political equality, ensuring that every citizen has a voice in the political discourse, these global forces present significant challenges. South Korea, characterized by swift economic growth and transformative political shifts, provides a critical context for exploring these challenges. These changes impact more than just the economy; they deeply influence the democratic ethos, raising crucial questions about the sustainability of political equality amidst pervasive transformations. Thus, the citizens of South Korea find themselves navigating an altered political and economic terrain, necessitating a critical reevaluation of democratic values in response to these global dynamics.

This paper delves into the significant question of how economic disparities and political transformations influence the democratic perceptions of South Korean citizens. By examining how global forces reflect in the populace's political engagement and representational sentiments, this study seeks to enrich our understanding of the contemporary democratic ethos in South Korea. To address these inquiries, this research utilizes data derived from a comprehensive questionnaire distributed to Korean citizens, capturing their perceptions of democracy and their participation in the democratic process. Employing linear regression models, the analysis focuses on identifying and interpreting the relationships between citizens' economic conditions, social contexts, and their democratic engagement. This methodological approach allows for a detailed exploration of how socio-economic factors influence perceptions and behaviours related to democracy in South Korea.

The findings of this study are vital for understanding the current state and future trajectory of democracy in regions undergoing rapid globalization. By highlighting how socio-economic disparities influence democratic engagement, this research offers insights that are crucial for policymakers, scholars, and citizens concerned with fostering a robust democratic society in the face of global changes. This paper is structured to first introduce the broader context and motivation, followed by an explanation of the data and methods used, presentation of the results, and a discussion that places these findings within the larger theoretical and practical frameworks of democracy and globalization.

This paper is structured to first provide a detailed literature review that sets the theoretical framework for understanding the impact of globalization on democratic values. Following this, @sec-data describes the survey design and analytical techniques employed. @sec-result present the analysis results, discuss the findings in the context of existing literature in @sec-discussion, and conclude with implications for policy and suggestions for future research. By offering a comprehensive exploration of how global trends and socio-economic transformations influence democratic perceptions and participation in South Korea, this study contributes valuable insights into the evolving nature of democracy in a globalized world.

# Data {#sec-data}
This project harnessed the capabilities of the statistical software, `R` [@citeR], throughout its execution. The `tidyverse` [@tidy] package was indispensable for data cleaning and manipulation tasks. The creation of figures and other data visualizations was adeptly handled using `ggplot2` [@ggplot2R], while `knitr` [@knitrR] and `kableExtra` [@kableextra] were utilized for their excellent data presentation features. File path management was conducted with `readr` [@readrR], and `rstanarm` [@rstanarm] was employed for statistical modeling, along with the `palmerpenguins` [@palmerpenguins] for illustrative purposes.

The data used in this study comes from the "Voter Political Consciousness Survey" conducted in South Korea following the 20th presidential election in 2016, under the auspices of The Comparative Study of Electoral Systems (CSES), a collaborative research project among national election studies worldwide. In this questionnaire, voters disclosed their economic and political perceptions. The raw dataset was large and unwieldy, so it was manually cleaned and renamed for readability. Variables were renamed as follows: E1006_NAM for the country name, E2002 for gender, E2001_Y for birth year, E3023 for satisfaction with democracy, E3007 for corruption, E3009 for political perception, and E3011 for economic perception. Unnecessary rows were deleted from the dataset.

## Data Summary

As show in @tbl-variables, the dependent variable will be based on the question, "On the whole, are you very satisfied, fairly satisfied, not very satisfied, or not at all satisfied with the way democracy works in South Korea?" The responses are coded on a four-point scale: 1. very satisfied, 2. fairly satisfied, 3. not very satisfied, and 4. not at all satisfied. For the independent variables, key variables on economic satisfaction will include responses to the question, "Would you say that over the past twelve months, the state of the economy in South Korea has gotten much better, gotten somewhat better, stayed about the same, gotten somewhat worse, or gotten much worse?" Answers are coded as 1. Gotten better, 2. stayed the same, 3. gotten worse, 4. don’t know. Additionally, perceptions of corruption will be assessed with the question, "How widespread do you think corruption such as bribe taking is among politicians in South Korea?" Responses are coded as 1. Very widespread, 2. Quite widespread, 3. Not very widespread, 4. It hardly happens at all, 8. Don’t know (Don’t read). Lastly, data on political changes will be obtained from the question regarding the performance of President Geun-hye Park's government: "Now thinking about the performance of the government of Geun-hye Park president in general, how good or bad a job do you think the government of Geun-hye Park president did over the past three years? Has she done a very good job?" Political satisfaction responses are coded as 1. Very good job, 2. Good job, 3. Bad job, 4. Very bad job.

```{r}
#| label: tbl-variables
#| tbl-cap: Summary of Variables
#| echo: false
#| warning: false

library(knitr)
library(kableExtra)

# Create the data frame with the variable summary
variable_summary <- data.frame(
  Types = c("The dependent variable", "The independent variables", "", ""),
  Variables = c("Satisfaction_With_Democracy", "Economic_Perception", "Corruption_Perception", "Political_Perception"),
  Criterion = c(
    "1. Very satisfied, 2. Fairly satisfied, 3. Not very satisfied, 4. Not at all satisfied",
    "1. Gotten better, 2. Stayed the same, 3. Gotten worse, 4. Don’t know",
    "1. Very widespread, 2. Quite widespread, 3. Not very widespread, 4. It hardly happens at all, 8. Don’t know",
    "1. Very good job, 2. Good job, 3. Bad job, 4. Very bad job"
  )
)

kable(variable_summary, booktabs = TRUE, escape = FALSE) %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = F, position = "left") %>%
  column_spec(1, width = "3cm") %>%  
  column_spec(2, width = "5cm") %>% 
  column_spec(3, width = "7cm")
```

## Data Analysis
To further explore the variables, summary statistics will be presented to describe the relationships among them. @fig-gender-perceptions will show how men and women in South Korea perceive the state of the economy, corruption, and political state. @fig-age-perceptions will show how different generational layers in South Korea perceive the state of the economy, corruption, and political state.

In the @fig-gender-perceptions , we have a set of three bar graphs, each representing a different type of perception—Corruption, Economic, and Political. The bars are divided by gender, with one colour representing male respondents (labelled as '1') and another color representing female respondents (labelled as '2'). The y-axis shows the average perception score, which likely corresponds to a survey response scale. Each bar's height indicates the average score for that perception type among the respective gender group. For instance, we can infer from the graph that both genders have similar average scores for corruption perception, while there may be slight differences in economic and political perceptions.

```{r}
#| label: fig-gender-perceptions
#| fig-cap: Perceptions by Gender
#| echo: false
#| warning: false

# Load necessary libraries
library(ggplot2)
library(dplyr)
library(readr)

# Load the data
analysis_data <- read_csv("/Users/hailey/Desktop/How_South_Koreans_View_Democracy/data/analysis_data/analysis_data.csv")

# Convert birth year to age since the data is obtained from 2016 (the survey year)
analysis_data$Age <- 2016 - analysis_data$Age

# Group age into intervals for better visualization
analysis_data$AgeGroup <- cut(analysis_data$Age, breaks=seq(min(analysis_data$Age), max(analysis_data$Age) + 10, by=10), right=FALSE)

analysis_data_long <- pivot_longer(analysis_data, 
                                   cols = c("Economic_Perception", "Corruption_Perception", "Political_Perception"), 
                                   names_to = "Perception_Type", 
                                   values_to = "Perception_Score")

# Plotting Perceptions by Gender
ggplot(analysis_data_long, aes(x = factor(Gender), y = Perception_Score, fill = factor(Gender))) +
  geom_bar(stat = "summary", fun = mean, position = position_dodge()) +
  facet_wrap(~Perception_Type, scales = "free_y") +
  labs(x = "Gender", y = "Average Perception Score") +
  theme_minimal()
```

In the @fig-age-perceptions, the same three types of perceptions are displayed. This time, however, they are categorized by age group, which are shown on the x-axis and range from [19,29] to [79,89]. These age groups are likely in ten-year increments, reflecting a broad categorization of respondents by age. The bars are colour-coded by age group, with each colour corresponding to a different age bracket. Similar to the first graph, the y-axis shows the average perception score. This graph illustrates how perceptions change across different age groups. For example, we can observe trends such as whether younger or older age groups rate economic, corruption, or political perceptions higher or lower on average, which might indicate generational differences in attitudes towards these issues.

```{r}
#| label: fig-age-perceptions
#| fig-cap: Perceptions by Age Group
#| echo: false
#| warning: false

# Load necessary libraries
library(ggplot2)
library(dplyr)
library(readr)

# Load the data
analysis_data <- read_csv("/Users/hailey/Desktop/How_South_Koreans_View_Democracy/data/analysis_data/analysis_data.csv")

# Plotting Perceptions by Age Group
ggplot(analysis_data_long, aes(x = AgeGroup, y = Perception_Score, fill = AgeGroup)) +
  geom_bar(stat = "summary", fun = mean, position = position_dodge()) +
  facet_wrap(~Perception_Type, scales = "free_y") +
  labs(x = "Age Group", y = "Average Perception Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 55, hjust = 1))  # Rotate the x-axis labels
```

These figures collectively aim to shed light on the distribution of attitudes towards different aspects of democratic society among different demographic groups in South Korea. The variation in average scores across different genders and age groups may suggest underlying social or cultural factors that influence how different groups perceive economic conditions, the prevalence of corruption, and political performance.

# Model

## Model set-up

In the Bayesian linear regression model[@rstanarm], we attempt to predict $Satisfaction\_With\_Democracy$ (the dependent variable, denoted as $y_i$ for each observation $i$) using $Economic\_Perception$, $Corruption\_Perception$, and $Political\_Perception$ as independent variables. The $y_i$ values are assumed to be normally distributed with a mean of $\mu_i$ and a common standard deviation $\sigma$. The mean $\mu_i$ is a linear combination of the independent variables, represented by the equation $\mu_i = \beta_0 + \beta_1 \cdot Economic\_Perception_i + \beta_2 \cdot Corruption\_Perception_i + \beta_3 \cdot Political\_Perception_i$. Here, $\beta_0$ is the intercept, the expected value of $Satisfaction\_With\_Democracy$ when all independent variables are at zero, reflecting a baseline level of satisfaction without the influence of the predictors. The coefficients $\beta_1$, $\beta_2$, and $\beta_3$ are the slopes that measure the expected change in $Satisfaction\_With\_Democracy$ for a one-unit change in their respective independent variables, assuming other variables are held constant. These regression coefficients are assumed to follow normal distributions with means of zero and standard deviations of 2.5, indicating that before observing the data, we believe it is equally likely that the variables could have a positive or negative association with satisfaction, with a moderate level of certainty. The standard deviation $\sigma$ of the dependent variable's distribution captures the variability of $Satisfaction\_With\_Democracy$ around its mean that is not explained by the independent variables. An Exponential prior with a rate of 1 is assigned to $\sigma$, which suggests we expect smaller values of $\sigma$ (indicating less noise) to be more likely than larger ones. This setup of priors and the model framework allow us to incorporate prior beliefs and uncertainties about the parameters, which are then updated with the data to provide a posterior distribution reflecting our updated beliefs.

\begin{align*}
y_i &\sim \text{Normal}(\mu_i, \sigma) \\
\mu_i &= \beta_0 + \beta_1 x_i \\
\beta_0 &\sim \text{Normal}(0, 2.5) \\
\beta_1 &\sim \text{Normal}(0, 2.5) \\
\sigma &\sim \text{Exponential}(1)
\end{align*}

### Model justification

# Result{#sec-result}

By examining the statistical analysis of @tbl-modelresults, we can explore the impact of economic and political changes on the formation of citizens' perceptions. The results of the two models indicate that perceptions of corruption and economics do not significantly influence the formation of perceptions regarding the realization of democracy. However, it was observed that political satisfaction does have a meaningful effect on the formation of democratic realization perceptions. Considering that political perception has a positive relationship with the perception of democratic realization, it can be interpreted that people who perceive a high level of political satisfaction have a positive perception of the realization of democracy.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
second_model <-
  readRDS(file = here::here("models/second_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model,
    "Second model" = second_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion{#sec-discussion}

## Democracy Perception by Different Variables {#sec-first-point}
@fig-economic-perceptions is a scatter plot overlaid with a linear regression trend line, depicting the relationship between Economic Perception and Satisfaction with Democracy. Each dot represents an individual observation from the dataset, with the horizontal axis (x-axis) representing the level of Economic Perception and the vertical axis (y-axis) indicating the level of Satisfaction with Democracy.

The outcome of the graph suggests that there is a positive association between Economic Perception and Satisfaction with Democracy. As Economic Perception increases, so does Satisfaction with Democracy, at least to some extent according to the data points and the upward trend of the regression line. The strength of this association, however, would need to be quantified with a correlation coefficient or by examining the regression coefficients from a statistical model output.
```{r}
#| label: fig-economic-perceptions
#| fig-cap: Democracy Perceptions by Economic Satisfaction
#| echo: false
#| warning: false

# Load the necessary libraries
library(ggplot2)
library(readr)

analysis_data <- read_csv("/Users/hailey/Desktop/How_South_Koreans_View_Democracy/data/analysis_data/analysis_data.csv")

# Satisfaction_With_Democracy and Economic_Perception
ggplot(analysis_data, aes(x = Economic_Perception, y = Satisfaction_With_Democracy)) +
  geom_point(alpha = 0.6) + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x = "Economic Perception", y = "Satisfaction with Democracy") +
  theme_minimal()
```

@fig-Corruption-perceptions shows a negative trend, indicated by the downward-sloping line, suggesting that as negative view of corruption levels in South Korea increases, Satisfaction with Democracy decreases. This outcome is somewhat expected, as higher perceptions of corruption are often associated with lower satisfaction with government institutions and democratic processes.

```{r}
#| label: fig-Corruption-perceptions
#| fig-cap: Democracy Perceptions by Corruption Perception
#| echo: false
#| warning: false

ggplot(analysis_data, aes(x = Corruption_Perception, y = Satisfaction_With_Democracy)) +
  geom_point(alpha = 0.6) + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x = "Corruption Perception", y = "Satisfaction with Democracy") +
  theme_minimal()
```

In contrast, the @fig-political-perceptions depicts a positive relationship between Political Satisfaction and Satisfaction with Democracy, as shown by the upward-sloping line. This suggests that lower levels of Political satisfaction, which may reflect a more favorable view of the political environment or political performance, are associated with increased Satisfaction with Democracy.

```{r}
#| label: fig-political-perceptions
#| fig-cap: Democracy Perceptions by Political Perception
#| echo: false
#| warning: false

ggplot(analysis_data, aes(x = Political_Perception, y = Satisfaction_With_Democracy)) +
  geom_point(alpha = 0.6) + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x = "Political Perception", y = "Satisfaction with Democracy") +
  theme_minimal()
```

## Democracy Perception

```{r}
#| label: fig-relationship-between-perceptions
#| fig-cap: Democracy Perceptions by All Factors
#| echo: false
#| warning: false

library(ggplot2)
library(dplyr)
library(readr)

analysis_data <- read_csv("/Users/hailey/Desktop/How_South_Koreans_View_Democracy/data/analysis_data/analysis_data.csv")

ggplot(analysis_data, aes(x = Economic_Perception, y = Satisfaction_With_Democracy)) +
  geom_point(aes(color = "Economic_Perception")) +
  geom_smooth(method = "lm", aes(color = "Economic_Perception"), se = FALSE) +
  geom_point(aes(x = Political_Perception, color = "Political_Perception")) +
  geom_smooth(method = "lm", aes(x = Political_Perception, color = "Political_Perception"), se = FALSE) +
  geom_point(aes(x = Corruption_Perception, color = "Corruption_Perception")) +
  geom_smooth(method = "lm", aes(x = Corruption_Perception, color = "Corruption_Perception"), se = FALSE) +
  labs(x = "Perception Score", y = "Satisfaction With Democracy", color = "Perception Type") +
  scale_color_manual(values = c("blue", "green", "red")) +
  theme_minimal()
```

## Conclusions

This research harnessed the analytical power of regression modeling to delve into how perceptions of economic and political shifts influence democratic sensibilities. It unveils a telling paradox: as dissatisfaction with economic and political conditions heightens, so too does the clamor for a more equitable democracy. Conversely, the heightened perception of corruption in Korea tends to dampen democratic sentiment, revealing a widespread disaffection with the governing structures—echoing themes prevalent in much of the current literature. This study's broader significance lies in its nuanced approach, shifting the lens from broad economic trends and institutional stability to the intricate fabric of individual perceptions. By doing so, it offers a granular view of democratic perceptions, tracing the subtle patterns that emerge from the interplay of personal economic and political experiences.

However, this research is not without its limitations. The regression model successfully identified prevailing perceptual trends within the confines of the data but fell short of illuminating the intricate web of interdependencies among these variables. While the study maps out the landscape of tendencies undergirding the three key variables, it stops short of uncovering the deeper, interwoven connections. As such, the path forward for subsequent inquiries is clear: to unearth the elusive threads that bind these insights into a cohesive narrative, furthering our understanding of the forces that shape democratic participation in the face of societal change.

\appendix

# Appendix {-}

# Additional data details

Other variables in the primary dataset

# Model details {#sec-model-details}

## Posterior predictive check

## Interval

\newpage

# References

### 2024-04-18 paper/paper.qmd
update

@@
 ---
-title: "Exploring Democratic Perceptions in South Korea"
+title: "How South Koreans View Democracy?"
 subtitle: "An Analysis of Survey Data in 2016"

### 2024-04-18 paper/paper.qmd
updating model

@@
 date-format: long
-abstract: "This study explores the impact of globalization on democratic values and participation in South Korea by employing a linear regression model to analyze responses from a nationwide questionnaire on citizens' perceptions and engagement.
-It found that economic disparities and transformative political changes significantly influence citizens’ views on democracy and their participation levels.
-Through this quantitative analysis, the research uncovers a complex relationship between socio-economic factors and democratic perception, demonstrating how economic inequalities can diminish feelings of representation and reduce democratic participation.
-These findings underscore the importance of addressing economic and social inequalities to foster a more inclusive and participative democratic environment in South Korea, contributing to our broader understanding of how globalization shapes political systems worldwide."
+abstract: "This study explores the impact of globalization on democratic values in South Korea by employing a linear regression model to analyze responses from a nationwide questionnaire on citizens' perceptions.
+Through the quantitative analysis, the research uncovers a complex relationship between diverse factors and democratic perception, demonstrating how political dissatisfaction can diminish feelings of representation and reduce democratic participation.
+These findings underscore the importance of addressing economic and political dissatisfaction to foster a more inclusive and participative democratic environment in South Korea, contributing to our broader understanding of how globalization shapes political systems worldwide."
 format: pdf
@@
 
-This paper delves into the significant question of how economic disparities and political transformations influence the democratic perceptions of South Korean citizens.
+This paper delves into the significant question of how economic and political dissatisfaction influence the democratic perceptions of South Korean citizens.
 By examining how global forces reflect in the populace's political engagement and representational sentiments, this study seeks to enrich our understanding of the contemporary democratic ethos in South Korea.
-To address these inquiries, this research utilizes data derived from a comprehensive questionnaire distributed to Korean citizens, capturing their perceptions of democracy and their participation in the democratic process.
-Employing linear regression models, the analysis focuses on identifying and interpreting the relationships between citizens' economic conditions, social contexts, and their democratic engagement.
+To address these inquiries, this research utilizes data derived from a comprehensive questionnaire distributed to Korean citizens, capturing their perceptions of economic and political aspects.
+Employing linear regression models, the analysis focuses on identifying and interpreting the relationships between citizens' economic conditions, political contexts, and their democratic engagement.
 This methodological approach allows for a detailed exploration of how socio-economic factors influence perceptions and behaviours related to democracy in South Korea.
@@
 The findings of this study are vital for understanding the current state and future trajectory of democracy in regions undergoing rapid globalization.
-By highlighting how socio-economic disparities influence democratic engagement, this research offers insights that are crucial for policymakers, scholars, and citizens concerned with fostering a robust democratic society in the face of global changes.
-This paper is structured to first introduce the broader context and motivation, followed by an explanation of the data and methods used, presentation of the results, and a discussion that places these findings within the larger theoretical and practical frameworks of democracy and globalization.
+By highlighting how socio-economic dissatisfaction influence democratic engagement, this research offers insights that are crucial for policymakers, scholars, and citizens concerned with fostering a robust democratic society in the face of global changes.
 
@@
 don’t know.
-Additionally, perceptions of corruption will be assessed with the question, "How widespread do you think corruption such as bribe taking is among politicians in South Korea?" Responses are coded as 1.
-Very widespread, 2.
-Quite widespread, 3.
-Not very widespread, 4.
-It hardly happens at all, 8.
-Don’t know (Don’t read).
-Lastly, data on political changes will be obtained from the question regarding the performance of President Geun-hye Park's government: "Now thinking about the performance of the government of Geun-hye Park president in general, how good or bad a job do you think the government of Geun-hye Park president did over the past three years?
+Additionally, perceptions of corruption will be assessed with the question, "Most politicians are trustworthy." Responses are coded as 1.
+Strongly agree, 2.
+Somewhat agree, 3.
+Neither, 4.
+Somewhat disagree, 5.
+Strongly disagree.
+Lastly, data on political changes will be obtained from the question regarding the performance of President Geun-hye Park's government in 2016: "Now thinking about the performance of the government of Geun-hye Park president in general, how good or bad a job do you think the government of Geun-hye Park president did over the past three years?
 Has she done a very good job?" Political satisfaction responses are coded as 1.
@@
   Types = c("The dependent variable", "The independent variables", "", ""),
-  Variables = c("Satisfaction_With_Democracy", "Economic_Perception", "Corruption_Perception", "Political_Perception"),
+  Variables = c("Dissatisfaction with democracy", "Dissatisfaction with economy", "Distrust level agianst politicians", "Dissatisfaction with politics"),
   Criterion = c(
@@
     "1. Gotten better, 2. Stayed the same, 3. Gotten worse, 4. Don’t know",
-    "1. Very widespread, 2. Quite widespread, 3. Not very widespread, 4. It hardly happens at all, 8. Don’t know",
+    "1. Strongly agree, 2. Somewhat agree, 3. Neither, 4. Somewhat disagree, 5. Strongly disagree",
     "1. Very good job, 2. Good job, 3. Bad job, 4. Very bad job"
@@
 kable(variable_summary, booktabs = TRUE, escape = FALSE) %>%
-  kable_styling(bootstrap_options = c("condensed"), full_width = F, position = "left") %>%
-  column_spec(1, width = "3cm") %>%  
+  kable_styling(bootstrap_options = c("condensed"), full_width = F, position = "center") %>%
+  column_spec(1, width = "2cm") %>%  
   column_spec(2, width = "5cm") %>% 
@@
 
-In the @fig-gender-perceptions , we have a set of three bar graphs, each representing a different type of perception—Corruption, Economic, and Political.
+In the @fig-gender-perceptions , we have a set of three bar graphs, each representing a different type of distrust level agianst Korean politicians, dissatisfaction of economy and politics.
 The bars are divided by gender, with one colour representing male respondents (labelled as '1') and another color representing female respondents (labelled as '2').
@@
 Each bar's height indicates the average score for that perception type among the respective gender group.
-For instance, we can infer from the graph that both genders have similar average scores for corruption perception, while there may be slight differences in economic and political perceptions.
+Both genders have similar average scores for economic dissatisfaction, while there may be slight differences in distrust against politicians and political dissatisfaction.
 
@@
 # Load the data
-analysis_data <- read_csv("/Users/hailey/Desktop/How_South_Koreans_View_Democracy/data/analysis_data/analysis_data.csv")
-
-# Convert birth year to age since the data is obtained from 2016 (the survey year)
-analysis_data$Age <- 2016 - analysis_data$Age
-
-# Group age into intervals for better visualization
-analysis_data$AgeGroup <- cut(analysis_data$Age, breaks=seq(min(analysis_data$Age), max(analysis_data$Age) + 10, by=10), right=FALSE)
+analysis_data <- read_csv("/Users/hailey/Desktop/Democracy_Perception_in_South_Korea/data/analysis_data/analysis_data.csv")
 
 analysis_data_long <- pivot_longer(analysis_data, 
-                                   cols = c("Economic_Perception", "Corruption_Perception", "Political_Perception"), 
+                                   cols = c("Dissatisfaction_with_economy", "Distrust_level_agianst_politicians", "Dissatisfaction_with_politics"), 
                                    names_to = "Perception_Type", 
                                    values_to = "Perception_Score")
+
+short_names <- c("Dissatisfaction_with_economy" = "Eco. Dissat.",
+                 "Distrust_level_agianst_politicians" = "Pol. Distrust",
+                 "Dissatisfaction_with_politics" = "Pol. Dissat.")
+
+analysis_data_long$Perception_Type <- factor(analysis_data_long$Perception_Type,
+                                             levels = names(short_names),
+                                             labels = short_names[names(short_names)])
+
+analysis_data_long$Gender <- factor(analysis_data_long$Gender, labels = c("Male", "Female"))
 
@@
   labs(x = "Gender", y = "Average Perception Score") +
-  theme_minimal()
+  theme_minimal() +
+  theme(axis.text.x = element_blank())
 ```
@@
 In the @fig-age-perceptions, the same three types of perceptions are displayed.
-This time, however, they are categorized by age group, which are shown on the x-axis and range from [19,29] to [79,89].
-These age groups are likely in ten-year increments, reflecting a broad categorization of respondents by age.
-The bars are colour-coded by age group, with each colour corresponding to a different age bracket.
-Similar to the first graph, the y-axis shows the average perception score.
-This graph illustrates how perceptions change across different age groups.
-For example, we can observe trends such as whether younger or older age groups rate economic, corruption, or political perceptions higher or lower on average, which might indicate generational differences in attitudes towards these issues.
+This time, however, they are categorized by birth year, which are shown on the x-axis and range from 1931 to 1997.
+The darkness of the bars corresponds to age, with darker shades representing older age groups.The @fig-age-perceptions suggest a view of generational sentiments: while economic and political dissatisfaction remain relatively consistent across age groups, there is a notable divergence when it comes to distrust in politicians.
+The younger generations who exhibit higher levels of distrust indicates a growing skepticism about political figures among newer generations compared to their older counterparts.
+This shift could reflect the evolving political landscape and the impact of recent events on the trust levels of different age groups.
 
@@
 
-# Load necessary libraries
 library(ggplot2)
@@
 library(readr)
+library(tidyr)
 
 # Load the data
-analysis_data <- read_csv("/Users/hailey/Desktop/How_South_Koreans_View_Democracy/data/analysis_data/analysis_data.csv")
+analysis_data <- read_csv("/Users/hailey/Desktop/Democracy_Perception_in_South_Korea/data/analysis_data/analysis_data.csv")
 
-# Plotting Perceptions by Age Group
-ggplot(analysis_data_long, aes(x = AgeGroup, y = Perception_Score, fill = AgeGroup)) +
+analysis_data_long <- pivot_longer(analysis_data, 
+                                   cols = c("Dissatisfaction_with_economy", "Distrust_level_agianst_politicians", "Dissatisfaction_with_politics"), 
+                                   names_to = "Perception_Type", 
+                                   values_to = "Perception_Score")
+
+short_names <- c("Dissatisfaction_with_economy" = "Eco. Dissat.",
+                 "Distrust_level_agianst_politicians" = "Pol. Distrust",
+                 "Dissatisfaction_with_politics" = "Pol. Dissat.")
+
+analysis_data_long$Perception_Type <- factor(analysis_data_long$Perception_Type,
+                                             levels = names(short_names),
+                                             labels = short_names[names(short_names)])
+
+ggplot(analysis_data_long, aes(x = Age, y = Perception_Score, fill = Age)) +
   geom_bar(stat = "summary", fun = mean, position = position_dodge()) +
@@
   theme_minimal() +
-  theme(axis.text.x = element_text(angle = 55, hjust = 1))  # Rotate the x-axis labels
+  theme(axis.text.x = element_text(angle = 55, hjust = 1))
 ```
@@
 
-By examining the statistical analysis of @tbl-modelresults, we can explore the impact of economic and political changes on the formation of citizens' perceptions.
+By examining the statistical analysis of @tbl-modelresults, we can explore the impact of economic and political satisfaction changes on the formation of citizens' perceptions.
 The results of the two models indicate that perceptions of corruption and economics do not significantly influence the formation of perceptions regarding the realization of democracy.
@@
 ## Democracy Perception by Different Variables {#sec-first-point}
-@fig-economic-perceptions is a scatter plot overlaid with a linear regression trend line, depicting the relationship between Economic Perception and Satisfaction with Democracy.
-Each dot represents an individual observation from the dataset, with the horizontal axis (x-axis) representing the level of Economic Perception and the vertical axis (y-axis) indicating the level of Satisfaction with Democracy.
+@fig-economic-perceptions is a scatter plot overlaid with a linear regression trend line, depicting the relationship between Economic dissatisfaction and dissatisfaction with Democracy.
 
-The outcome of the graph suggests that there is a positive association between Economic Perception and Satisfaction with Democracy.
-As Economic Perception increases, so does Satisfaction with Democracy, at least to some extent according to the data points and the upward trend of the regression line.
-The strength of this association, however, would need to be quantified with a correlation coefficient or by examining the regression coefficients from a statistical model output.
+The outcome of the graph suggests that there is a positive association between  dissatisfaction with economics and dissatisfaction with democracy, as indicated by the upward slope of the trend line.
+Points on the graph tend to shift from lighter to darker as they move right, suggesting that increased economic dissatisfaction correlates with a higher dissatisfaction with democracy, particularly as age increases.
+This could imply that older individuals, who potentially have more experience with economic fluctuations and political systems, might perceive a stronger link between economic and democratic dissatisfaction.
+
 ```{r}
@@
 
-analysis_data <- read_csv("/Users/hailey/Desktop/How_South_Koreans_View_Democracy/data/analysis_data/analysis_data.csv")
+# Load the data
+analysis_data <- read_csv("/Users/hailey/Desktop/Democracy_Perception_in_South_Korea/data/analysis_data/analysis_data.csv")
 
-# Satisfaction_With_Democracy and Economic_Perception
-ggplot(analysis_data, aes(x = Economic_Perception, y = Satisfaction_With_Democracy)) +
+ggplot(analysis_data, aes(x = Dissatisfaction_with_economy, y = Dissatisfaction_with_democracy, color = Age)) +
   geom_point(alpha = 0.6) + 
-  geom_smooth(method = "lm", se = FALSE) + 
-  labs(x = "Economic Perception", y = "Satisfaction with Democracy") +
-  theme_minimal()
+  geom_smooth(method = "lm", se = TRUE, color = "blue") +  
+  scale_color_viridis_c(option = "D") +  
+  labs(x = "Dissatisfaction with Economics", 
+       y = "Dissatisfaction with Democracy", 
+       title = "Democracy Perceptions by Economic Satisfaction") +
+  theme_minimal() +
+  theme(legend.position = "bottom")  
 ```
 
-@fig-Corruption-perceptions shows a negative trend, indicated by the downward-sloping line, suggesting that as negative view of corruption levels in South Korea increases, Satisfaction with Democracy decreases.
-This outcome is somewhat expected, as higher perceptions of corruption are often associated with lower satisfaction with government institutions and democratic processes.
+@fig-politicians-perceptions shows a correlation between mistrust in politicians and dissatisfaction with democracy, with a gradual upward trend line signifying that as mistrust against politicians increases, so does dissatisfaction with democracy.
+Notably, the younger age groups (lighter colors) seem to be concentrated at higher levels of mistrust, suggesting that younger individuals may be more inclined to distrust politicians and consequently feel more dissatisfied with democracy.
 
 ```{r}
-#| label: fig-Corruption-perceptions
+#| label: fig-politicians-perceptions
 #| fig-cap: Democracy Perceptions by Corruption Perception
@@
 
-ggplot(analysis_data, aes(x = Corruption_Perception, y = Satisfaction_With_Democracy)) +
+ggplot(analysis_data, aes(x = Distrust_level_agianst_politicians, y = Dissatisfaction_with_democracy, color = Age)) +
   geom_point(alpha = 0.6) + 
-  geom_smooth(method = "lm", se = FALSE) + 
-  labs(x = "Corruption Perception", y = "Satisfaction with Democracy") +
-  theme_minimal()
+  geom_smooth(method = "lm", se = TRUE, color = "blue") +  
+  scale_color_viridis_c(option = "D") +  
+  labs(x = "Mistrust against Politicians", 
+       y = "Dissatisfaction with Democracy") +
+  theme_minimal() +
+  theme(legend.position = "bottom")  
 ```
 
-In contrast, the @fig-political-perceptions depicts a positive relationship between Political Satisfaction and Satisfaction with Democracy, as shown by the upward-sloping line.
-This suggests that lower levels of Political satisfaction, which may reflect a more favorable view of the political environment or political performance, are associated with increased Satisfaction with Democracy.
+The @fig-political-perceptions displays a clear positive correlation between dissatisfaction with politics and dissatisfaction with democracy, indicated by the ascending trend line.
+As political dissatisfaction increases, so does dissatisfaction with democracy, suggesting that negative feelings towards the political system are closely linked with negative perceptions of democratic governance.
+The gradient color, representing age groups from older (darker) to younger (lighter), reveals a relatively even distribution across the spectrum of political dissatisfaction, signifying that these sentiments are pervasive across different ages without a visible age-related trend in the data.
+This indicates a general consensus across generations regarding the relationship between political dissatisfaction and democratic discontent.
 
@@
 
-ggplot(analysis_data, aes(x = Political_Perception, y = Satisfaction_With_Democracy)) +
+ggplot(analysis_data, aes(x = Dissatisfaction_with_politics, y = Dissatisfaction_with_democracy, color = Age)) +
   geom_point(alpha = 0.6) + 
-  geom_smooth(method = "lm", se = FALSE) + 
-  labs(x = "Political Perception", y = "Satisfaction with Democracy") +
-  theme_minimal()
+  geom_smooth(method = "lm", se = TRUE, color = "blue") +  
+  scale_color_viridis_c(option = "D") +  
+  labs(x = "Dissatisfaction with Politics", 
+       y = "Dissatisfaction with Democracy") +
+  theme_minimal() +
+  theme(legend.position = "bottom")  
 ```
-
 ## Democracy Perception
+The @fig-slop-comparison illustrates the estimated slopes of three different regression models, each representing the impact of a specific type of dissatisfaction—economic, political, and distrust against politicians—on dissatisfaction with democracy.
+The plot reveals that all three factors have a positive relationship with dissatisfaction with democracy, as indicated by the fact that all the estimated coefficients are above zero.
+Economic dissatisfaction has the smallest estimated impact, whereas political dissatisfaction has the highest, with distrust against politicians falling in between.
+The vertical lines represent the confidence intervals for each estimate, and none of them cross the horizontal line at zero, suggesting that all three relationships are statistically significant.
+The differences in the lengths of these lines indicate varying degrees of certainty about the estimates, with economic dissatisfaction showing the widest interval, implying the least precision.
 
 ```{r}
-#| label: fig-relationship-between-perceptions
-#| fig-cap: Democracy Perceptions by All Factors
+#| label: fig-slop-comparison
+#| fig-cap: Comparison of Slopes from Different Regression Models
 #| echo: false
@@
 
-library(ggplot2)
 library(dplyr)
-library(readr)
+library(broom)
 
-analysis_data <- read_csv("/Users/hailey/Desktop/How_South_Koreans_View_Democracy/data/analysis_data/analysis_data.csv")
+# Assuming analysis_data is already loaded and contains the variables
+# Fit separate linear models for each factor
+models <- list(
+  econ = lm(Dissatisfaction_with_democracy ~ Dissatisfaction_with_economy, data = analysis_data),
+  pol = lm(Dissatisfaction_with_democracy ~ Dissatisfaction_with_politics, data = analysis_data),
+  trust = lm(Dissatisfaction_with_democracy ~ Distrust_level_agianst_politicians, data = analysis_data)
+)
 
-ggplot(analysis_data, aes(x = Economic_Perception, y = Satisfaction_With_Democracy)) +
-  geom_point(aes(color = "Economic_Perception")) +
-  geom_smooth(method = "lm", aes(color = "Economic_Perception"), se = FALSE) +
-  geom_point(aes(x = Political_Perception, color = "Political_Perception")) +
-  geom_smooth(method = "lm", aes(x = Political_Perception, color = "Political_Perception"), se = FALSE) +
-  geom_point(aes(x = Corruption_Perception, color = "Corruption_Perception")) +
-  geom_smooth(method = "lm", aes(x = Corruption_Perception, color = "Corruption_Perception"), se = FALSE) +
-  labs(x = "Perception Score", y = "Satisfaction With Democracy", color = "Perception Type") +
-  scale_color_manual(values = c("blue", "green", "red")) +
+# Extract the coefficients with confidence intervals
+model_coefficients <- bind_rows(
+  lapply(models, function(model) {
+    tidy(model, conf.int = TRUE) %>%
+      filter(term != "(Intercept)") # Remove the intercept
+  }),
+  .id = "model"
+)
+
+# Rename the factor levels for better graph labeling
+model_coefficients$model <- factor(model_coefficients$model, levels = c("econ", "pol", "trust"),
+                                   labels = c("Economic Dissatisfaction", "Political Dissatisfaction", "Distrust Against Politicians"))
+
+# Plot the coefficient for each model
+ggplot(model_coefficients, aes(x = model, y = estimate, ymin = conf.low, ymax = conf.high)) +
+  geom_pointrange() +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  labs(x = "Factor", y = "Estimated Slope (Coefficient)") +
   theme_minimal()
@@
 
-This research harnessed the analytical power of regression modeling to delve into how perceptions of economic and political shifts influence democratic sensibilities.
-It unveils a telling paradox: as dissatisfaction with economic and political conditions heightens, so too does the clamor for a more equitable democracy.
-Conversely, the heightened perception of corruption in Korea tends to dampen democratic sentiment, revealing a widespread disaffection with the governing structures—echoing themes prevalent in much of the current literature.
-This study's broader significance lies in its nuanced approach, shifting the lens from broad economic trends and institutional stability to the intricate fabric of individual perceptions.
-By doing so, it offers a granular view of democratic perceptions, tracing the subtle patterns that emerge from the interplay of personal economic and political experiences.
+The study presents an examination of how socio-economic and political dissatisfaction influence the democratic sentiments of South Koreans amidst the multifaceted challenges of globalization.
+By utilizing linear regression models to parse out the effects of these variables on democratic contentment, it delineates a clear pattern where political dissatisfaction holds the most sway in eroding democratic satisfaction, outpacing the influence of distrust in politicians and economic dissatisfaction.
+These findings illuminate the critical role of political harmony and economic stability in underpinning the health of a democracy.
+As South Korea faces the winds of global change, such insights are vital for crafting policies that shore up democratic integrity and public trust.
 
-However, this research is not without its limitations.
-The regression model successfully identified prevailing perceptual trends within the confines of the data but fell short of illuminating the intricate web of interdependencies among these variables.
-While the study maps out the landscape of tendencies undergirding the three key variables, it stops short of uncovering the deeper, interwoven connections.
-As such, the path forward for subsequent inquiries is clear: to unearth the elusive threads that bind these insights into a cohesive narrative, furthering our understanding of the forces that shape democratic participation in the face of societal change.
-
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
-Other variables in the primary dataset
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-## Interval
+However, the research is not without limitations.
+It operates on the assumption that the survey responses accurately reflect the intricate reality of individual perceptions, which may not encapsulate the full spectrum of socio-political nuances.
+The methodology, while robust, cannot account for unmeasured variables that may confound the relationships explored.
+Furthermore, the cross-sectional nature of the survey data limits the ability to draw causal inferences.
+Despite these weaknesses, the study contributes significantly to our understanding of democracy in a rapidly evolving socio-economic landscape.
+It beckons a call for future research to adopt longitudinal approaches and consider a broader array of variables, thereby enriching the discourse on sustaining democratic values amidst the complexities of the modern world.
 

### 2024-04-18 scripts/02-data_cleaning.R

@@ -21,7 +21,7 @@ data <- read_csv("data/raw_data/raw_data.csv", col_types = cols(
   E2002 = col_double(),
   E2001_Y = col_double(),
   E3023 = col_double(),
-  E3007 = col_double(),
+  E3004_3 = col_double(),
   E3009 = col_double(),
   E3011 = col_double()
 ))
@@ -29,19 +29,31 @@ data <- read_csv("data/raw_data/raw_data.csv", col_types = cols(
 data <- as.data.frame(data)
 
 cleaned_data <- data %>%
-  dplyr::select(E1006_NAM, E2002, E2001_Y, E3023, E3007, E3009, E3011)
+  dplyr::select(E1006_NAM, E2002, E2001_Y, E3023, E3004_3, E3009, E3011)
 
 # Rename the columns to more descriptive names
 cleaned_data <- cleaned_data %>%
   rename(
-    Country_Name = E1006_NAM,
+    Country = E1006_NAM,
     Gender = E2002,
     Age = E2001_Y,
-    Satisfaction_With_Democracy = E3023,
-    Economic_Perception = E3011,
-    Corruption_Perception = E3007,
-    Political_Perception = E3009
+    Dissatisfaction_with_democracy = E3023,
+    Dissatisfaction_with_economy = E3011,
+    Distrust_level_agianst_politicians = E3004_3,
+    Dissatisfaction_with_politics = E3009
   )
 
 #### Save data ####
 write_csv(cleaned_data, "data/analysis_data/analysis_data.csv")
+
+data <- read_csv("data/analysis_data/analysis_data.csv")
+
+# Filter out rows where Corruption_Perception or Economic_Perception is 8 (don't know)
+filtered_data <- data %>%
+  filter(Dissatisfaction_with_economy != 8 & Distrust_level_agianst_politicians != 8)
+
+head(filtered_data)
+
+#### Save data ####
+write_csv(filtered_data, "data/analysis_data/analysis_data.csv")
+

### 2024-04-18 scripts/03-test_data.R

@@ -24,7 +24,7 @@ cleaned_data %>%
 
 # Boxplot for Satisfaction with Democracy
 cleaned_data %>%
-  ggplot(aes(x = "", y = Satisfaction_With_Democracy)) +
+  ggplot(aes(x = "", y = Dissatisfaction_with_democracy)) +
   geom_boxplot(fill = "cyan", color = "black") +
   labs(title = "Boxplot of Satisfaction with Democracy", x = "", y = "Satisfaction Level") +
   theme_minimal()
@@ -34,12 +34,4 @@ cleaned_data %>%
   ggplot(aes(x = as.factor(Gender))) +
   geom_bar(fill = "magenta") +
   labs(title = "Gender Distribution", x = "Gender", y = "Count") +
-  theme_minimal()
-
-# Density Plot for Attitudes About Elites: Important to Seek Compromise
-cleaned_data %>%
-  ggplot(aes(x = Attitudes_About_Elites_Compromise)) +
-  geom_density(fill = "orange", alpha = 0.7) +
-  labs(title = "Density Plot of Attitudes About Elites: Important to Seek Compromise",
-       x = "Attitude Scale", y = "Density") +
   theme_minimal()

### 2024-04-18 scripts/04-model.R

@@ -18,7 +18,7 @@ analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
 
 first_model <-
   stan_glm(
-    formula = Satisfaction_With_Democracy ~ Corruption_Perception + Economic_Perception + Political_Perception,
+    formula = Dissatisfaction_with_democracy ~ Distrust_level_agianst_politicians + Dissatisfaction_with_economy + Dissatisfaction_with_politics,
     data = analysis_data,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
@@ -29,11 +29,11 @@ first_model <-
 
 second_model <-
   stan_glm(
-    formula = Satisfaction_With_Democracy ~ Corruption_Perception + Economic_Perception + Political_Perception,
+    formula = Dissatisfaction_with_democracy ~ Distrust_level_agianst_politicians + Dissatisfaction_with_economy + Dissatisfaction_with_politics,
     data = analysis_data,
     family = gaussian(),
-    prior = normal(location = 0, scale = 1, autoscale = TRUE), # Tighter prior for coefficients
-    prior_intercept = normal(location = 0, scale = 1, autoscale = TRUE), # Tighter prior for intercept
+    prior = normal(location = 0, scale = 1, autoscale = TRUE), 
+    prior_intercept = normal(location = 0, scale = 1, autoscale = TRUE), 
     prior_aux = exponential(rate = 1, autoscale = TRUE),
     seed = 853
   )
@@ -48,3 +48,4 @@ saveRDS(
   second_model,
   file = "models/second_model.rds"
 )
+

### 2024-04-18 paper/paper.qmd
Update the writing from paper

@@
 South Korea, characterized by swift economic growth and transformative political shifts, provides a critical context for exploring these challenges.
-These changes impact more than just the economy; they deeply influence the democratic ethos, raising crucial questions about the sustainability of political equality amidst pervasive transformations.
+These changes impact more than just the economy; they deeply influence the democratic ethos, raising crucial questions about the sustainability of political equality amidst pervasive transformations [@article].
 Thus, the citizens of South Korea find themselves navigating an altered political and economic terrain, necessitating a critical reevaluation of democratic values in response to these global dynamics.

### 2024-04-19 paper/paper.qmd
Update files after the few changes from data simulation

@@
 ---
-title: "How South Koreans View Democracy?"
-subtitle: "An Analysis of Survey Data in 2016"
+title: "Perceptions of Democracy in South Korea"
+subtitle: "Insights from 2016 Survey Data"
 author: 
   - Hailey Jang 
-thanks: "Code and data are available at: https://github.com/Hailey-Jang/How_South_Koreans_View_Democracy.git."
+thanks: "Code and data are available at: https://github.com/Hailey-Jang/Democracy_Perception_in_South_Korea.git."
 date: today
@@
 This paper delves into the significant question of how economic and political dissatisfaction influence the democratic perceptions of South Korean citizens.
-By examining how global forces reflect in the populace's political engagement and representational sentiments, this study seeks to enrich our understanding of the contemporary democratic ethos in South Korea.
-To address these inquiries, this research utilizes data derived from a comprehensive questionnaire distributed to Korean citizens, capturing their perceptions of economic and political aspects.
-Employing linear regression models, the analysis focuses on identifying and interpreting the relationships between citizens' economic conditions, political contexts, and their democratic engagement.
-This methodological approach allows for a detailed exploration of how socio-economic factors influence perceptions and behaviours related to democracy in South Korea.
+To address our understanding of the contemporary democratic ethos in South Korea, this research utilizes data derived from a comprehensive questionnaire distributed to Korean citizens in 2016, capturing their perceptions of economic and political aspects.
+Employing linear regression models, the analysis focuses on identifying and interpreting the relationships between citizens' economic conditions and political contexts.
+This methodological approach allows for a detailed exploration of political satisfaction influence perceptions and behaviours related to democracy in South Korea.
 
@@
 This paper is structured to first provide a detailed literature review that sets the theoretical framework for understanding the impact of globalization on democratic values.
-Following this, @sec-data describes the survey design and analytical techniques employed.
-@sec-result present the analysis results, discuss the findings in the context of existing literature in @sec-discussion, and conclude with implications for policy and suggestions for future research.
-By offering a comprehensive exploration of how global trends and socio-economic transformations influence democratic perceptions and participation in South Korea, this study contributes valuable insights into the evolving nature of democracy in a globalized world.
+Following this, @sec-data and @sec-model describes the survey design and analytical techniques by conducting linear regression model.
+@sec-result present the analysis results, discuss the findings in the context of existing literature in @sec-discussion, and @sec-conclusion with implications for weakness and suggestions for future research.
 
 # Data {#sec-data}
-This project harnessed the capabilities of the statistical software, `R` [@citeR], throughout its execution.
-The `tidyverse` [@tidy] package was indispensable for data cleaning and manipulation tasks.
-The creation of figures and other data visualizations was adeptly handled using `ggplot2` [@ggplot2R], while `knitr` [@knitrR] and `kableExtra` [@kableextra] were utilized for their excellent data presentation features.
-File path management was conducted with `readr` [@readrR], and `rstanarm` [@rstanarm] was employed for statistical modeling, along with the `palmerpenguins` [@palmerpenguins] for illustrative purposes.
+This project used `R` [@citeR] throughout its execution.
+The `tidyverse` [@tidy] package was utilized for data cleaning and manipulation tasks.
+The creation of figures and other data visualizations was adeptly handled using `ggplot2` [@ggplot2R], while `knitr` [@knitrR] and `kableExtra` [@kableextra] were used for their excellent data presentation features.
+File path management was conducted with `readr` [@readrR], and `rstanarm` [@rstanarm] was employed for statistical modeling, along with the `broom` [@robinson] for illustrative purposes.
 
@@
 
-In the @fig-gender-perceptions , we have a set of three bar graphs, each representing a different type of distrust level agianst Korean politicians, dissatisfaction of economy and politics.
+In the @fig-gender-perceptions, we have a set of three bar graphs, each representing a different type of distrust level agianst Korean politicians, dissatisfaction of economy and politics.
 The bars are divided by gender, with one colour representing male respondents (labelled as '1') and another color representing female respondents (labelled as '2').
@@
 These figures collectively aim to shed light on the distribution of attitudes towards different aspects of democratic society among different demographic groups in South Korea.
-The variation in average scores across different genders and age groups may suggest underlying social or cultural factors that influence how different groups perceive economic conditions, the prevalence of corruption, and political performance.
+The variation in average scores across different genders and age groups may suggest underlying social or cultural factors that influence how different groups perceive economic conditions and political performance.
+Next, we will explore how these factors relate to their democratic perception through linear regression model.
 
-# Model
+# Model {#sec-model}
 
@@
 
-### Model justification
-
 # Result{#sec-result}
 
-By examining the statistical analysis of @tbl-modelresults, we can explore the impact of economic and political satisfaction changes on the formation of citizens' perceptions.
-The results of the two models indicate that perceptions of corruption and economics do not significantly influence the formation of perceptions regarding the realization of democracy.
-However, it was observed that political satisfaction does have a meaningful effect on the formation of democratic realization perceptions.
-Considering that political perception has a positive relationship with the perception of democratic realization, it can be interpreted that people who perceive a high level of political satisfaction have a positive perception of the realization of democracy.
+By examining the statistical analysis of @tbl-modelresults, we can explore the impact of economic and political dissatisfaction changes on the formation of citizens' perceptions.
+The results of the two models indicate that perceptions of politicians and economics do not significantly influence the formation of perceptions regarding the realization of democracy.
+However, it was observed that political dissatisfaction does have a meaningful effect on the formation of democratic realization perceptions.
+Considering that political perception has a positive relationship with the perception of democratic realization, it can be interpreted that people who perceive a high level of political dissatisfaction have a negative perception of democracy.
 
@@
 
-# Discussion{#sec-discussion}
-
-## Democracy Perception by Different Variables {#sec-first-point}
+## Democracy Perception by Different Variables 
 @fig-economic-perceptions is a scatter plot overlaid with a linear regression trend line, depicting the relationship between Economic dissatisfaction and dissatisfaction with Democracy.
@@
 ```
+
 ## Democracy Perception
@@
 
-## Conclusions
+# Discussion{#sec-discussion}
 

### 2024-04-19 scripts/00-simulate_data.R

@@ -13,21 +13,21 @@ library(dplyr)
 country_names <- c("Republic of Korea") 
 genders <- c(1, 2)  # 1 for Male, 2 for Female
 satisfaction_levels <- 1:5
-corruption_levels <- 1:8
+Distrusts_levels <- 1:5
 political_levels <- 1:5
-economic_levels <- 1:8
+economic_levels <- 1:4
 age_range <- 1931:1997
 
 # Function to simulate data
-simulate_data <- function(n) {
+simulated_data <- function(n) {
   data_frame(
     Country_Name = sample(country_names, n, replace = TRUE),
     Gender = sample(genders, n, replace = TRUE),
     Age = sample(age_range, n, replace = TRUE),
-    Satisfaction_With_Democracy = sample(satisfaction_levels, n, replace = TRUE),
-    Corruption_Perception = sample(corruption_levels, n, replace = TRUE),
-    Political_Perception = sample(political_levels, n, replace = TRUE),
-    Economic_Perception = sample(economic_levels, n, replace = TRUE)
+    Dissatisfaction_with_democracy = sample(satisfaction_levels, n, replace = TRUE),
+    Distrust_level_agianst_politician = sample(Distrusts_levels, n, replace = TRUE),
+    Dissatisfaction_with_politics = sample(political_levels, n, replace = TRUE),
+    Dissatisfaction_with_economy = sample(economic_levels, n, replace = TRUE)
   )
 }
 

### 2024-04-19 paper/paper.qmd
final update after reviewing paper

@@
 Following this, @sec-data and @sec-model describes the survey design and analytical techniques by conducting linear regression model.
-@sec-result present the analysis results, discuss the findings in the context of existing literature in @sec-discussion, and @sec-conclusion with implications for weakness and suggestions for future research.
+@sec-result present the analysis results, discuss the findings in the context of existing literature in @sec-discussion with implications for weakness and suggestions for future research.
 
@@
 
-In the Bayesian linear regression model[@rstanarm], we attempt to predict $Satisfaction\_With\_Democracy$ (the dependent variable, denoted as $y_i$ for each observation $i$) using $Economic\_Perception$, $Corruption\_Perception$, and $Political\_Perception$ as independent variables.
+In the Bayesian linear rewgression model[@rstanarm], we attempt to predict $Dissatisfaction\_With\_Democracy$ (the dependent variable, denoted as $y_i$ for each observation $i$) using $Distrust\_level\_against\_politicians$, $Dissatisfaction\_with\_economy$, and $Dissatisfaction\_with\_politics$ as independent variables.
 The $y_i$ values are assumed to be normally distributed with a mean of $\mu_i$ and a common standard deviation $\sigma$.
-The mean $\mu_i$ is a linear combination of the independent variables, represented by the equation $\mu_i = \beta_0 + \beta_1 \cdot Economic\_Perception_i + \beta_2 \cdot Corruption\_Perception_i + \beta_3 \cdot Political\_Perception_i$.
-Here, $\beta_0$ is the intercept, the expected value of $Satisfaction\_With\_Democracy$ when all independent variables are at zero, reflecting a baseline level of satisfaction without the influence of the predictors.
-The coefficients $\beta_1$, $\beta_2$, and $\beta_3$ are the slopes that measure the expected change in $Satisfaction\_With\_Democracy$ for a one-unit change in their respective independent variables, assuming other variables are held constant.
+The mean $\mu_i$ is a linear combination of the independent variables, represented by the equation $\mu_i = \beta_0 + \beta_1 \cdot Dissatisfaction\_with\_economy_i + \beta_2 \cdot Distrust\_level\_against\_politicians_i + \beta_3 \cdot Dissatisfaction\_with\_politics_i$.
+Here, $\beta_0$ is the intercept, the expected value of $Dissatisfaction\_with\_politics$ when all independent variables are at zero, reflecting a baseline level of satisfaction without the influence of the predictors.
+The coefficients $\beta_1$, $\beta_2$, and $\beta_3$ are the slopes that measure the expected change in $Dissatisfaction\_with\_politics$ for a one-unit change in their respective independent variables, assuming other variables are held constant.
 These regression coefficients are assumed to follow normal distributions with means of zero and standard deviations of 2.5, indicating that before observing the data, we believe it is equally likely that the variables could have a positive or negative association with satisfaction, with a moderate level of certainty.
-The standard deviation $\sigma$ of the dependent variable's distribution captures the variability of $Satisfaction\_With\_Democracy$ around its mean that is not explained by the independent variables.
+The standard deviation $\sigma$ of the dependent variable's distribution captures the variability of $Dissatisfaction\_with\_politics$ around its mean that is not explained by the independent variables.
 An Exponential prior with a rate of 1 is assigned to $\sigma$, which suggests we expect smaller values of $\sigma$ (indicating less noise) to be more likely than larger ones.

### 2024-04-19 other/datasheet/datasheet_template.qmd
update after change of datasheet

---
title: "Datasheet for 'Perceptions of Democracy in South Korea'"
author: 
  - Hailey Jang
thanks: "Code and data are available at: https://github.com/Hailey-Jang/Democracy_Perception_in_South_Korea.git."
date: today
format: pdf
number-sections: true
---

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*

- The dataset was created to explore the impact of globalization on democratic values in South Korea. Specifically, it aimed to understand how economic and political dissatisfaction influence the democratic perceptions of South Korean citizens. The research utilized a comprehensive questionnaire distributed in 2016, focusing on citizens' perceptions of economic and political aspects. The purpose was to address the contemporary democratic ethos in South Korea using a linear regression model to analyze the relationships between citizens' economic conditions and political contexts.

2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*

- The dataset was compiled under the auspices of The Comparative Study of Electoral Systems (CSES), a collaborative research project among national election studies worldwide. It utilized responses from the “Voter Political Consciousness Survey” conducted following the 20th presidential election in 2016 in South Korea.

3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*

- The document does not specifically mention who funded the creation of the dataset. However, since the dataset was used under the Comparative Study of Electoral Systems (CSES), it is likely that it was supported through the framework of this international research project.

4. *Any other comments?*

- The study emphasizes the significance of addressing economic and political dissatisfaction to foster a more inclusive and participative democratic environment in South Korea. It highlights the importance of such research in contributing to a broader understanding of how globalization shapes political systems worldwide.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*

- The dataset consists of survey responses from individual participants. The instances represent individual entries in the survey, primarily capturing political and socio-economic perceptions related to elections in South Korea.

2. *How many instances are there in total (of each type, if appropriate)?*

- The specific total number of instances (individual survey responses) in the dataset is 119.

3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*

- The dataset is a sample of responses from the broader population of voters in South Korea, derived from the “Voter Political Consciousness Survey.” It aims to be representative of the population’s political consciousness among 119 citiznes.

4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*

- Each instance contains a large number of features (605 columns), which include both coded survey responses and some metadata (e.g., survey version, DOI). Data types include integers, floating-point numbers, and strings, suggesting a mixture of quantitative answers, categorical data, and identifiers.

5. *Is there a label or target associated with each instance? If so, please provide a description.*

- The dataset includes labels associated with each instance, primarily the levels of satisfaction or dissatisfaction with democracy and the economy, perceptions of corruption, and political performance. These are derived from survey responses and coded into numerical scales

6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*

- While the initial preview doesn't explicitly show missing values, some entries like '9999999' or '9999996' in certain columns may represent coded missing data or specific survey coding for non-responses or non-applicable answers.

7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- There is no specific relationships between individual instances

8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- There is no information provided about recommended splits for training, validation, or testing within this dataset. Usage would depend on the specific research design.

9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- Given the complex nature of survey data, errors or redundancies might exist, but cannot be definitively identified without further detailed analysis or access to the survey design documentation.

10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset contains metadata linking to external standards or documentation (e.g., DOI links), suggesting reliance on external definitions or protocols for data collection and coding. No information about the permanence or changes over time for these resources is available from the dataset alone.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- The dataset appears to handle personal perceptions and opinions which are generally anonymized; however, direct information about confidentiality protections isn't available in the dataset preview.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- There is no indication from the preview that the dataset contains offensive or insulting data. It focuses on political and economic perceptions.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- The dataset likely categorizes respondents by demographic factors such as age or gender, which are common in survey datasets. Exact distributions would require further analysis.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- Without more detailed metadata, it is unclear if individuals could be indirectly identified; the dataset appears to be anonymized for general research use.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- The dataset contains politically sensitive information, such as voting behavior and political opinions, which could be considered sensitive. Other sensitive demographic information might also be included.
16. *Any other comments?*
	- To fully leverage this dataset, detailed documentation on the survey methodology, question coding, and data cleaning procedures would be necessary for accurate analysis and interpretation.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was reported by subjects through a survey. Such data is directly reported by the participants and typically involves questions related to political, economic, and social perceptions. Validation or verification of this kind of self-reported data is often limited to consistency checks and logical validation (e.g., ensuring responses fall within the allowed range).
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Data collection for surveys is typically done using paper forms where respondents enter their answers. The validation of these mechanisms usually involves pre-testing the survey (pilot testing) to ensure questions are understood as intended and the data collection system works smoothly.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The dataset likely employed a probabilistic sampling method to ensure representativeness of the South Korean electorate, but specifics such as the exact method (stratified, random, etc.) require access to the survey methodology documentation.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Such surveys are generally conducted by research teams or through survey firms. Compensation details for these personnel would depend on the employment or contract terms but are typically salaried positions or contracted services.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The data was collected following the 20th presidential election in 2016 in South Korea. The creation timeframe matches the survey's focus, aiming to capture contemporary political consciousness around that period.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- For studies involving human subjects, especially on sensitive topics like political opinions, ethical review approval (e.g., from an Institutional Review Board) is commonly required. This process would ensure that the study complies with ethical standards, though specific details would be documented in the associated study protocols.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was collected directly from individuals through the survey process, not obtained via third parties or secondary sources.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- Participants in such surveys are typically notified about the study's purpose at the time of survey administration. This notification would include information about the survey's scope, the organization conducting it, and how the data will be used.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- Consent to participate in the survey would have been obtained at the time of data collection, usually through a consent form or verbal agreement after explaining the survey's purpose and use of the data. The exact language of consent would typically emphasize voluntary participation and the confidentiality of responses.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- If provided, mechanisms to revoke consent would be detailed in the consent form, allowing participants to withdraw from the study at any time. This might be more relevant in longitudinal studies than in one-time surveys.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- An analysis like a data protection impact analysis is crucial for sensitive data but is not often detailed in the dataset itself. Such analysis would assess risks related to data handling and privacy implications.
12. *Any other comments?*
	- For a comprehensive understanding and responsible use of the dataset, access to the full survey documentation, ethical approvals, and data handling protocols would be necessary. These documents would provide deeper insights into the dataset's integrity and appropriateness for specific types of analysis.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- While the specific document doesn't detail the usage of this dataset, datasets similar to this one are typically used in political science and sociology research to analyze voter behavior, perceptions of democracy, and the influence of political events on public opinion. They might also be utilized in studies assessing the impact of economic conditions on political attitudes or the effectiveness of governmental policies.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- https://github.com/Hailey-Jang/Democracy_Perception_in_South_Korea.git
3. *What (other) tasks could the dataset be used for?*
	- Beyond political analysis, this dataset could serve educational purposes in teaching statistical analysis, political science, or data science methodologies. It could also be used in predictive modeling to forecast election results or public opinion trends based on demographic and historical data. Additionally, NGOs or policymakers might analyze the data to better understand public needs or responses to governance.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- Users of the dataset should be aware of potential biases introduced during the data collection or preprocessing stages. For instance, non-response bias or sampling errors can skew results, potentially leading to misrepresentations of certain populations. To mitigate these risks, users should perform rigorous statistical tests to check for representativeness and bias and apply corrective measures like weighting or stratification where applicable. They should also be transparent about any limitations of the data when publishing findings to avoid misleading interpretations.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- The dataset should not be used for any purposes that could potentially harm individuals, such as targeting vulnerable groups based on political opinions or creating discriminatory policies. It's also inappropriate to use this data for commercial purposes that could infringe on the privacy or rights of the individuals who participated in the survey, especially without explicit consent covering those uses.
6. *Any other comments?*
	- Future researchers and users of the dataset should ensure compliance with ethical guidelines and legal standards, particularly regarding data privacy and protection. Regular reviews and updates to the dataset documentation can help maintain its relevance and usefulness, addressing any emerging ethical or legal issues. Collaboration with domain experts in political science can enhance the reliability and applicability of research findings derived from the dataset.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The supporting entity would usually be the academic institution or research group that conducted the survey. Their ongoing commitment to maintaining the dataset would depend on funding and research priorities.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- Typically provided through the dataset's main documentation or via the research group's webpage.You can contact via `https://cses.org/`
3. *Is there an erratum? If so, please provide a link or other access point.*
	-Any updates would likely be communicated through academic publications or updates to the repository where the dataset is hosted. The process would involve the original research team or a designated data curator.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- Limits on data retention would be especially important for sensitive data, and would typically be governed by ethical guidelines or legal requirements related to data protection (e.g., GDPR). Documentation should detail how these aspects are managed.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- Mechanisms for external contributions would be rare for such datasets, but if allowed, would likely require thorough validation to maintain data integrity and reliability.

### 2024-04-19 scripts/02-data_cleaning.R
Update 02-data_cleaning.R

@@ -11,6 +11,7 @@
 library(tidyverse)
 library(readr)
 library(dplyr)
+library(arrow)
 
 
 #### Clean data ####
@@ -56,4 +57,5 @@ head(filtered_data)
 
 #### Save data ####
 write_csv(filtered_data, "data/analysis_data/analysis_data.csv")
+write_parquet(filtered_data, "data/analysis_data/analysis_data.parquet")
 

### 2024-04-19 paper/paper.qmd
Update paper.qmd

@@
 ---
-title: "Perceptions of Democracy in South Korea"
+title: "Diminishing Democratic Ethos in South Korea by Political Dissatisfaction"
 subtitle: "Insights from 2016 Survey Data"
@@
 
-In South Korea, a nation where I was born and raised, the rapid and profound impacts of globalization have redefined the socio-economic and political landscape.
+In South Korea, a nation where I was born and raised, the rapid and profound impacts of globalization have redefined the socioeconomic and political landscape.
 As democracy inherently upholds the principle of political equality, ensuring that every citizen has a voice in the political discourse, these global forces present significant challenges.
@@
 
-This paper delves into the significant question of how economic and political dissatisfaction influence the democratic perceptions of South Korean citizens.
+This paper delves into the significant question of how economic and political dissatisfaction influences the democratic perceptions of South Korean citizens.
 To address our understanding of the contemporary democratic ethos in South Korea, this research utilizes data derived from a comprehensive questionnaire distributed to Korean citizens in 2016, capturing their perceptions of economic and political aspects.
 Employing linear regression models, the analysis focuses on identifying and interpreting the relationships between citizens' economic conditions and political contexts.
-This methodological approach allows for a detailed exploration of political satisfaction influence perceptions and behaviours related to democracy in South Korea.
+This methodological approach allows for a detailed exploration of how political satisfaction influences perceptions and behaviours related to democracy in South Korea.
 
 The findings of this study are vital for understanding the current state and future trajectory of democracy in regions undergoing rapid globalization.
-By highlighting how socio-economic dissatisfaction influence democratic engagement, this research offers insights that are crucial for policymakers, scholars, and citizens concerned with fostering a robust democratic society in the face of global changes.
+By highlighting how socioeconomic dissatisfaction influences democratic engagement, this research offers insights that are crucial for policymakers, scholars, and citizens concerned with fostering a robust democratic society in the face of global changes.
 
 This paper is structured to first provide a detailed literature review that sets the theoretical framework for understanding the impact of globalization on democratic values.
-Following this, @sec-data and @sec-model describes the survey design and analytical techniques by conducting linear regression model.
-@sec-result present the analysis results, discuss the findings in the context of existing literature in @sec-discussion with implications for weakness and suggestions for future research.
+Following this, @sec-data and @sec-model describe the survey design and analytical techniques by conducting a linear regression model.
+@sec-result presents the analysis results, and discusses the findings in the context of existing literature in @sec-discussion with implications for weakness and suggestions for future research.
 
@@
 The creation of figures and other data visualizations was adeptly handled using `ggplot2` [@ggplot2R], while `knitr` [@knitrR] and `kableExtra` [@kableextra] were used for their excellent data presentation features.
-File path management was conducted with `readr` [@readrR], and `rstanarm` [@rstanarm] was employed for statistical modeling, along with the `broom` [@robinson] for illustrative purposes.
+File path management was conducted with `readr` [@readrR], and `rstanarm` [@rstanarm] was employed for statistical modelling, along with the `broom` [@robinson] for illustrative purposes.
 
@@
 
-As show in @tbl-variables, the dependent variable will be based on the question, "On the whole, are you very satisfied, fairly satisfied, not very satisfied, or not at all satisfied with the way democracy works in South Korea?" The responses are coded on a four-point scale: 1.
+As shown in @tbl-variables, the dependent variable will be based on the question, "On the whole, are you very satisfied, fairly satisfied, not very satisfied, or not at all satisfied with the way democracy works in South Korea?" The responses are coded on a four-point scale: 1.
 very satisfied, 2.
@@
   Types = c("The dependent variable", "The independent variables", "", ""),
-  Variables = c("Dissatisfaction with democracy", "Dissatisfaction with economy", "Distrust level agianst politicians", "Dissatisfaction with politics"),
+  Variables = c("Dissatisfaction with democracy", "Dissatisfaction with economy", "Distrust level against politicians", "Dissatisfaction with politics"),
   Criterion = c(
@@
 
-In the @fig-gender-perceptions, we have a set of three bar graphs, each representing a different type of distrust level agianst Korean politicians, dissatisfaction of economy and politics.
-The bars are divided by gender, with one colour representing male respondents (labelled as '1') and another color representing female respondents (labelled as '2').
+In the @fig-gender-perceptions, we have a set of three bar graphs, each representing a different type of distrust level against Korean politicians, and dissatisfaction of economy and politics.
+The bars are divided by gender, with one colour representing male respondents (labelled as '1') and another colour representing female respondents (labelled as '2').
 The y-axis shows the average perception score, which likely corresponds to a survey response scale.
-Each bar's height indicates the average score for that perception type among the respective gender group.
+Each bar's height indicates the average score for that perception type among the respective gender groups.
 Both genders have similar average scores for economic dissatisfaction, while there may be slight differences in distrust against politicians and political dissatisfaction.
@@
 In the @fig-age-perceptions, the same three types of perceptions are displayed.
-This time, however, they are categorized by birth year, which are shown on the x-axis and range from 1931 to 1997.
-The darkness of the bars corresponds to age, with darker shades representing older age groups.The @fig-age-perceptions suggest a view of generational sentiments: while economic and political dissatisfaction remain relatively consistent across age groups, there is a notable divergence when it comes to distrust in politicians.
-The younger generations who exhibit higher levels of distrust indicates a growing skepticism about political figures among newer generations compared to their older counterparts.
+This time, however, they are categorized by birth year, which is shown on the x-axis and ranges from 1931 to 1997.
+The darkness of the bars corresponds to age, with darker shades representing older age groups.
+The @fig-age-perceptions suggest a view of generational sentiments: while economic and political dissatisfaction remain relatively consistent across age groups, there is a notable divergence when it comes to distrust in politicians.
+The younger generations who exhibit higher levels of distrust indicate a growing skepticism about political figures among newer generations compared to their older counterparts.
 This shift could reflect the evolving political landscape and the impact of recent events on the trust levels of different age groups.
@@
 The variation in average scores across different genders and age groups may suggest underlying social or cultural factors that influence how different groups perceive economic conditions and political performance.
-Next, we will explore how these factors relate to their democratic perception through linear regression model.
+Next, we will explore how these factors relate to their democratic perception through the linear regression model.
 
@@
 
-In the Bayesian linear rewgression model[@rstanarm], we attempt to predict $Dissatisfaction\_With\_Democracy$ (the dependent variable, denoted as $y_i$ for each observation $i$) using $Distrust\_level\_against\_politicians$, $Dissatisfaction\_with\_economy$, and $Dissatisfaction\_with\_politics$ as independent variables.
+In the Bayesian linear regression model[@rstanarm], we attempt to predict $Dissatisfaction\_With\_Democracy$ (the dependent variable, denoted as $y_i$ for each observation $i$) using $Distrust\_level\_against\_politicians$, $Dissatisfaction\_with\_economy$, and $Dissatisfaction\_with\_politics$ as independent variables.
 The $y_i$ values are assumed to be normally distributed with a mean of $\mu_i$ and a common standard deviation $\sigma$.
@@
 As political dissatisfaction increases, so does dissatisfaction with democracy, suggesting that negative feelings towards the political system are closely linked with negative perceptions of democratic governance.
-The gradient color, representing age groups from older (darker) to younger (lighter), reveals a relatively even distribution across the spectrum of political dissatisfaction, signifying that these sentiments are pervasive across different ages without a visible age-related trend in the data.
+The gradient colour, representing age groups from older (darker) to younger (lighter), reveals a relatively even distribution across the spectrum of political dissatisfaction, signifying that these sentiments are pervasive across different ages without a visible age-related trend in the data.
 This indicates a general consensus across generations regarding the relationship between political dissatisfaction and democratic discontent.
@@
 
-# Rename the factor levels for better graph labeling
+# Rename the factor levels for better graph labelling
 model_coefficients$model <- factor(model_coefficients$model, levels = c("econ", "pol", "trust"),

### 2024-04-19 paper/paper.qmd
Update paper.qmd

--- 2024-04-19 paper/paper.qmd
@@
 
-In South Korea, a nation where I was born and raised, the rapid and profound impacts of globalization have redefined the socio-economic and political landscape.
+In South Korea, a nation where I was born and raised, the rapid and profound impacts of globalization have redefined the socio-economic and political factors.
 As democracy inherently upholds the principle of political equality, ensuring that every citizen has a voice in the political discourse, these global forces present significant challenges.
 South Korea, characterized by swift economic growth and transformative political shifts, provides a critical context for exploring these challenges.
-These changes impact more than just the economy; they deeply influence the democratic ethos, raising crucial questions about the sustainability of political equality amidst pervasive transformations [@article].
+These changes impact more than just the economy; they deeply influence the democratic ethos, raising important questions about the sustainability of political equality amidst pervasive transformations [@article].
 Thus, the citizens of South Korea find themselves navigating an altered political and economic terrain, necessitating a critical reevaluation of democratic values in response to these global dynamics.
 
-This paper delves into the significant question of how economic and political dissatisfaction influence the democratic perceptions of South Korean citizens.
-To address our understanding of the contemporary democratic ethos in South Korea, this research utilizes data derived from a comprehensive questionnaire distributed to Korean citizens in 2016, capturing their perceptions of economic and political aspects.
+This paper will explore the significant question of how economic and political dissatisfaction influence the democratic perceptions of South Korean citizens.
+To address our understanding of the contemporary democratic ethos in South Korea, this research utilizes data derived from a questionnaire distributed to Korean citizens in 2016, capturing their perceptions of economic and political aspects.
 Employing linear regression models, the analysis focuses on identifying and interpreting the relationships between citizens' economic conditions and political contexts.
@@
 The findings of this study are vital for understanding the current state and future trajectory of democracy in regions undergoing rapid globalization.
-By highlighting how socio-economic dissatisfaction influence democratic engagement, this research offers insights that are crucial for policymakers, scholars, and citizens concerned with fostering a robust democratic society in the face of global changes.
+By highlighting how socio-economic dissatisfaction influence democratic engagement, this research offers insights that are important for policymakers, scholars, and citizens concerned with fostering a powerful democratic society in the face of global changes.
 
@@
 The y-axis shows the average perception score, which likely corresponds to a survey response scale.
-Each bar's height indicates the average score for that perception type among the respective gender group.
+Each bar's height indicates the average score for that perception type among the respective gender groups.
 Both genders have similar average scores for economic dissatisfaction, while there may be slight differences in distrust against politicians and political dissatisfaction.
@@
 In the @fig-age-perceptions, the same three types of perceptions are displayed.
-This time, however, they are categorized by birth year, which are shown on the x-axis and range from 1931 to 1997.
-The darkness of the bars corresponds to age, with darker shades representing older age groups.The @fig-age-perceptions suggest a view of generational sentiments: while economic and political dissatisfaction remain relatively consistent across age groups, there is a notable divergence when it comes to distrust in politicians.
-The younger generations who exhibit higher levels of distrust indicates a growing skepticism about political figures among newer generations compared to their older counterparts.
-This shift could reflect the evolving political landscape and the impact of recent events on the trust levels of different age groups.
+This time, however, they are categorized by birth year, which is shown on the x-axis and ranges from 1931 to 1997.
+The darkness of the bars corresponds to age, with darker shades representing older age groups.
+The @fig-age-perceptions suggest a view of generational sentiments: while economic and political dissatisfaction remain relatively consistent across age groups, there is a notable divergence when it comes to distrust in politicians.
+The younger generations who exhibit higher levels of distrust indicate a growing skepticism about political figures among newer generations compared to their older counterparts.
+This shift could reflect the evolving political sector and the impact of recent events on the trust levels of different age groups.
 
@@
 
-These figures collectively aim to shed light on the distribution of attitudes towards different aspects of democratic society among different demographic groups in South Korea.
+These figures collectively aim to find out the distribution of attitudes towards different aspects of democratic society among different demographic groups in South Korea.
 The variation in average scores across different genders and age groups may suggest underlying social or cultural factors that influence how different groups perceive economic conditions and political performance.
@@
 @fig-politicians-perceptions shows a correlation between mistrust in politicians and dissatisfaction with democracy, with a gradual upward trend line signifying that as mistrust against politicians increases, so does dissatisfaction with democracy.
-Notably, the younger age groups (lighter colors) seem to be concentrated at higher levels of mistrust, suggesting that younger individuals may be more inclined to distrust politicians and consequently feel more dissatisfied with democracy.
+Notably, the younger age groups (lighter colours) seem to be concentrated at higher levels of mistrust, suggesting that younger individuals may be more inclined to distrust politicians and consequently feel more dissatisfied with democracy.
 
@@
 These findings illuminate the critical role of political harmony and economic stability in underpinning the health of a democracy.
-As South Korea faces the winds of global change, such insights are vital for crafting policies that shore up democratic integrity and public trust.
+As South Korea faces the winds of global change, such insights are vital for making policies that shore up democratic integrity and public trust.
 
 However, the research is not without limitations.
-It operates on the assumption that the survey responses accurately reflect the intricate reality of individual perceptions, which may not encapsulate the full spectrum of socio-political nuances.
-The methodology, while robust, cannot account for unmeasured variables that may confound the relationships explored.
+It operates on the assumption that the survey responses accurately reflect the complex reality of individual perceptions, which may not encapsulate the full spectrum of socio-political nuances.
+The methodology, while powerful, cannot account for unmeasured variables that may confound the relationships explored.
 Furthermore, the cross-sectional nature of the survey data limits the ability to draw causal inferences.
-Despite these weaknesses, the study contributes significantly to our understanding of democracy in a rapidly evolving socio-economic landscape.
+Despite these weaknesses, the study contributes significantly to our understanding of democracy in a rapidly evolving socio-economic sector.
 It beckons a call for future research to adopt longitudinal approaches and consider a broader array of variables, thereby enriching the discourse on sustaining democratic values amidst the complexities of the modern world.
